Universal and variable leadership dimensions across human societies

### 2020-06-24 leadership_across_cultures_contexts.Rmd
Back to HTML -- SUBMITTED VERSION

---
title: "Universal and varying leadership dimensions across human societies"
author: "Zachary H. Garfield, Kristen L. Syme, and Edward H. Hagen"
date: "4/25/2019"
output: 
  bookdown::html_document2:
    number_sections: true
bibliography: Leader2.bib
csl: apa-6th-edition.csl
---

@@

For each of our four factors, we then investigated which levels of the factor were associated with higher or lower levels of evidence for the leadership dimension. For instance, there were three dimensions in which subsistence strategy played an important role: *No coercive authority*, *Provide subsistence*, and *Distribute resources* (See Figure \@ref(fig:heatmapdrop1)). Hunter-gatherers had particularly high levels of evidence for *No coercive authority*, relative to other subsistence strategies (and averaging over levels of the other three factors), and pastoralists had relatively low evidence for *Distribute resources* (see Figure S\@ref(fig:heatmapsubsis)). For group context, region, and leader sex see Figures S\@ref(fig:heatmapgroups), S\@ref(fig:heatmapregion), and S\@ref(fig:heatmapsex).

@@

```{r elasticcoercive, fig.width=10, fig.height=10, fig.cap="Coefficients of logistic elasticnet regression models of evidence for *Coercive authority* and *No coercive authority*. A, C: Coefficients indicate the words whose frequencies in each text record best predicted evidence for *Coercive authority* and *No coercive authority, respectively, in each text record. B, D: Non-zero coefficients of all quality and function dimensions that best predicted evidence for *Coercive authority* and *No coercive authority, respectively. Both models used the lasso penalty ($\\alpha=1$) and chose $\\lambda_{1se}$ by cross-validation (1 SE from $\\lambda_{min}$). Red values are positive predictors; purple values are negative predictors. Predictors with coefficents = 0 not displayed. X-axes are odds ratios on a log 10 scale."}

>>>>

---
title: "Universal and variable leadership dimensions across human societies"
author: "Zachary H. Garfield, Kristen L. Syme, and Edward H. Hagen"
date: "4/25/2019"
output: 
  bookdown::html_document2:
    number_sections: true
bibliography: Leader2.bib
csl: apa-6th-edition.csl
---

@@

For each of our four factors, we then investigated which levels of the factor were associated with higher or lower levels of evidence for the leadership dimension. For instance, there were three dimensions in which subsistence strategy played an important role: *No coercive authority*, *Provide subsistence*, and *Distribute resources* (see Figure \@ref(fig:heatmapdrop1)). Hunter-gatherers had particularly high levels of evidence for *No coercive authority*, relative to other subsistence strategies (and averaging over levels of the other three factors), and pastoralists had relatively low evidence for *Distribute resources* (see Figure S\@ref(fig:heatmapsubsis)). For group context, region, and leader sex see Figures S\@ref(fig:heatmapgroups), S\@ref(fig:heatmapregion), and S\@ref(fig:heatmapsex).

@@

```{r elasticcoercive, fig.width=10, fig.height=10, fig.cap="Coefficients of logistic elasticnet regression models of evidence for *Coercive authority* and *No coercive authority*. A, C: Coefficients indicate the words whose frequencies in each text record best predicted evidence for *Coercive authority* and *No coercive authority, respectively, in each text record. B, D: Non-zero coefficients of all quality and function dimensions that best predicted evidence for *Coercive authority* and *No coercive authority*, respectively. Both models used the lasso penalty ($\\alpha=1$) and chose $\\lambda_{1se}$ by cross-validation (1 SE from $\\lambda_{min}$). Red values are positive predictors; purple values are negative predictors. Predictors with coefficents = 0 not displayed. X-axes are odds ratios on a log 10 scale."}
